Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-14 arxiv-version/main.tex
Small fixes

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
\forall i \in \{1,2,\dots,K\} \qquad \qquad \norm{w_i}^2 & \le 1 \; , \\
\label{equation:strong-linear-separability-2}
\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
\label{equation:strong-linear-separability-3}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
\end{align}
\end{definition}

@@

However, if $K=3$ there exists a set of labeled examples in an inner product
space that is linearly separable with a positive margin $\gamma$ but it is not
strongly linearly separable for any positive $\gamma$. This is best illustrated
on Figure~\ref{figure:linearly-separable-examples-with-margin}.

>>>>

The examples are said to be \emph{strongly linearly separable with a
margin $\gamma$} if there exist vectors $w_1, w_2, \dots, w_K \in V$ such
that
\begin{align}
\label{equation:strong-linear-separability-1}
\sum_{i=1}^K \norm{w_i}^2 & \le 1 \; , \\
\label{equation:strong-linear-separability-2}
\forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} &\ge \gamma \; , \\
\label{equation:strong-linear-separability-3}
\forall t \in \{1,2,\dots,T\} \qquad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \qquad \qquad \ip{x_t}{w_i} & \le - \gamma \; .
\end{align}
\end{definition}

@@

However, if $K \ge 3$ there exists a set of labeled examples in an inner product
space that is linearly separable with a positive margin $\gamma$ but it is not
strongly linearly separable for any positive $\gamma$. Such set of examples is
shown in Figure~\ref{figure:linearly-separable-examples-with-margin}.
